Data Analysis and Visualisation using R

### 2016-01-12 paper.tex
Include all code listing

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|}
\hline \bf Label & \bf Number of observations & \bf Predictor variables \\ \hline
ash & 500 & {\tt X1, X2, X3, X4, X5, X6, X7, X8, X9} \\ \hline
beech & 500 & {\tt X3, X7} \\ \hline
elder & 500 & {\tt X1, X2, X3, X4, X5, X6, X7, X8, X9} \\ \hline
elm & 100 & {\tt X1, X2, X3, X4, X5, X6, X7, X8, X9} \\ \hline
larch & 50 & {\tt X1, X2, X3, X4, X5, X6, X7, X8, X9} \\ \hline
oak & 50 & {\tt X1, X2, X3, X4, X5, X6, X7, X8, X9} \\ \hline
rowan & 50 & {\tt X1, X2, X3, X4, X5, X6, X7, X8, X9} \\ \hline
yew & 50 & {\tt X1, X2, X3, X4, X5, X6, X7, X8, X9} \\ \hline
\end{tabular}
\end{center}
\caption{\label{subset-table} Overview of subset in training data.}
\end{table}

@@

>>>>

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|}
\hline \bf Label & \bf Number of observations & \bf Predictor variables \\ \hline
ash & 500 & {\tt X1, X2, X3, X4, X5, X6, X7, X8, X9} \\ \hline
beech & 500 & {\tt X3, X7} \\ \hline
elder & 500 & {\tt X7} \\ \hline
elm & 100 & {\tt X3, X8} \\ \hline
larch & 50 & {\tt X3, X4, X5, X9} \\ \hline
oak & 50 & {\tt X3} \\ \hline
rowan & 50 & {\tt X4} \\ \hline
yew & 50 & {\tt X4} \\ \hline
\end{tabular}
\end{center}
\caption{\label{subset-table} Overview of subset in training data.}
\end{table}

@@

\lstinputlisting[breaklines=true,language=R,caption={elm.R},label=elm]{project/6-elm.R}

\lstinputlisting[breaklines=true,language=R,caption={larch.R},label=larch]{project/7-larch.R}

\lstinputlisting[breaklines=true,language=R,caption={oak.R},label=oak]{project/8-oak.R}

\lstinputlisting[breaklines=true,language=R,caption={rowan.R},label=rowan]{project/9-rowan.R}

\lstinputlisting[breaklines=true,language=R,caption={yew.R},label=yew]{project/10-yew.R}
